%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

%% \cventry
%% {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
%% {R.O.K Cyber Command, MND} % Organization
%% {Seoul, S.Korea} % Location
%% {Aug. 2014 - Exp. Apr. 2016} % Date(s)
%% { % Description(s) of tasks/responsibilities
%% \begin{cvitems}
%% \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
%% \item {Improved functionality on military command and control system for incident response with Java Servlet.}
%% \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
%% \end{cvitems}
%% }

%------------------------------------------------

\cventry
{Insight Capital Partners} % Job title
{Chief Data Scientist} % Organization
{London - U.K.} % Location
{2018 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Organize the Data Analytics / Data Science team and coordinate with the Operations and Data Acquisition departments.}
\item {Machine Learning applied to Investment Portfolio Management. Natural Language Processing of financial news.}
\item {Statistical consultancy. Devise and supervise data analysis and research as sevice for our customers.}
\item {Create automated Data Pipelines, from data ETL and sumarization to final report generation.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Barclays - Advanced Data Solutions Team} % Job title
{Senior Data Scientist} % Organization
{London - U.K.} % Location
{2017 - 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Supervising a team of 3. I implement machine learning pipelines for risk evaluation on millions of clients.}
\item {Building up recommend systems and customer segmentation analysis, enhancing data business value for marketing.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Genomics England Ltd. - Bioinformatics Department} % Job title
{Data Scientist} % Organization
{London - U.K.} % Location
{2015 - 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Modeling clinical and genomic data: 100K individuals, millions of variables (genetic variants).}
\item {Data visualization, automatic report writing, data scraping from SQL, MongoDB, Spark, web services and web pages.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Genometra S.L.} % Job title
{Founder and Head of Data Science} % Organization
{Valencia - Spain} % Location
{2010 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {I co-founded the company and supervised a team of 4. We developed machine learning software for diagnosis and.}
\item {Developed several R \& Python packages, web tools and distributed pipelines. Statistical consultancy.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{University of Valencia - Mathematics and Computer Science Departments} % Job title
{Part Time Lecturer} % Organization
{Valencia - Spain} % Location
{2009 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Teaching databases, R, Python and Bash programming, statistics and probability to undergrad and MSc students.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Principe Felipe Research Center (CIPF) - Computational Genomics Department} % Job title
{Head of the Biostatistics Unit} % Organization
{Valencia - Spain} % Location
{2005 - 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Written +50 scientific publications. Presented and organized +30 congresses and workshops. Supervised staff and students.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{University of Bristol - Social Medicine School} % Job title
{Epidemiologist} % Organization
{Bristol - U.K.} % Location
{2002 - 2004} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Preprocessing and statistical analysis of large cohort studies. Survival analysis, class prediction and hypothesis testing.} % 125 total
\end{cvitems}        
}

%------------------------------------------------

\end{cventries}
