%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

%% \cventry
%% {B.S. in Computer Science and Engineering} % Degree
%% {POSTECH(Pohang University of Science and Technology)} % Institution
%% {Pohang, S.Korea} % Location
%% {Mar. 2010 - PRESENT} % Date(s)
%% { % Description(s) bullet points
%% \begin{cvitems}
%% \item {Got a Chun Shin-Il Scholarship which is given to promising students in CSE Dept.}
%% \end{cvitems}
%% }

\cventry
{Universitat de Valencia - Biotechnology} % Degree
{PhD in Bioinformatics and Functional Genomics} % Institution
{Valencia - Spain} % Location
{2009 - 2013} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
I explored different statistical methodologies to push forward the knowledge in functional genomics.
The DNA sequence of most genes is known, but their function, how they act in the body, is generally undescribed. 
The aim was to be able to predict gene functionality form genetic experimental data.
}
\item {
I collected information from hundreds of different experiments publicly available.
I did preprocess them and standardize signals to get a data matrix of 25,000 genes and 30,000 experiments.
I did combine this experimental information with that of many databases describing gene functionality.
Then I tested several approaches to infer and analyze genetic function.
}
\item {
My final proposal used Multidimensional Logistic Regression to infer gene activity and functionality.
I used a weighed model which incorporated prior experimental information and corrected for gene colinearity and correlation.
My approach was also novel because it allowed for the interpretation of several genomic characteristics at the same time
(current methods work just with a single genetic dimension or measure set but there are many available)
}
\item {
I implemented the Methodology in an R package called mdgsa which is available in the Bioconductor repository.
The methodology was also used as a back end of the Babelomics web suit.
}
\end{cvitems}
}

\cventry
{Universidad Complutense de Madrid - Mathematics Department} % Degree
{MSc in Probability \& Statistics} % Institution   %% Diploma Estudios Avanzados (MSc) in Statistics
{Madrid - Spain} % Location
{2002 - 2004} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
I tackled the missing data imputation problem. 
I explored the EM algorithm in the context of multiple imputation,
I used bootstrap and some other resampling techniques for incomplete data analysis.
}
\end{cvitems}
}

\cventry
{University of Southampton - Statistics Department} % Degree
{MSc in Statistics with Applications in Medicine} % Institution   %% Diploma Estudios Avanzados (MSc) in Statistics
{Southampton - U.K.} % Location
{2001 - 2002} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Experimental design, stratification, sample size calculation, demographic analysis, clinical trials, spatial analysis.}
\end{cvitems}
}

\cventry
{Universidad Complutense de Madrid} % Degree
{Degree in Mathematics} % Institution   %% Diploma Estudios Avanzados (MSc) in Statistics
{Madrid - Spain} % Location
{1995 - 2001} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Statistics and Operations Research specialty.}
\end{cvitems}
}

%% \cventry{2013}      {PhD in Bioinformatics and Functional Genomics}    {\newline Universitat de Valencia}           {UNO}                       {DOS}{TRES}
%% \cventry{2002--2004}{Diploma Estudios Avanzados (MSc) in Statistics}   {\newline Universidad Complutense de Madrid} {Statistics Department}  {}{}
%% \cventry{2001--2002}{MSc in Statistics with Applications in Medicine}  {\newline University of Southampton}         {Mathematics Department} {(Erasmus program)}{}
%% \cventry{1995--2001}{Degree in Mathematics}                            {\newline Universidad Complutense de Madrid} {}                       {}{}

%------------------------------------------------

\end{cventries}
