%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

%% \cventry
%% {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
%% {R.O.K Cyber Command, MND} % Organization
%% {Seoul, S.Korea} % Location
%% {Aug. 2014 - Exp. Apr. 2016} % Date(s)
%% { % Description(s) of tasks/responsibilities
%% \begin{cvitems}
%% \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
%% \item {Improved functionality on military command and control system for incident response with Java Servlet.}
%% \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
%% \end{cvitems}
%% }

%------------------------------------------------

\cventry
{Genomics England Ltd. - Bioinformatics Department} % Job title
{Data Scientist} % Organization
{London - U.K.} % Location
{2015 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
Genomics England Ltd.
is the leading partner of the 
largest genomic consortium in the world:
the 100,000 Genomes Project.
}
\item {
My main duty is to model clinical and genomic data for 100,000 individuals and millions of variables (genetic variants) using R and Python.
I use supervised classification methods (SVM, KNN, LDA and Random forests)
to predict clinical outcomes from genomic variables.
The aim is for instance to discriminate cancer and normal samples,
classify different tumors or predict disease stages from the patient genetic information.
I also used logistic regression models to evaluate disease risk,
and Cox proportional hazards models for survival analysis.
}
\item {
I parsed and collected clinical information from hundreds of files in many different formats: XML, JSON, xls, csv.
I organized this information in our internal LabKey data management system (SQL).
I created an R library which calls LabKey web services to automatize the data intake.
I then collected genomic information stored in MongoDB, combined it with the clinical information,
and used our own Python libraries to serve it to our clients trough a REST API.
}
\item {
I computed descriptive statistics and using R and Python,
and created plots and visual representations of the data using the ggplot2 library.
I used unsupervised classification methods (KNN and hierarchical clustering)
and principal component analysis
to find out outliers and biases in our data.
I inserted those in automatically generated reports using
knitr, pandoc markdown and LaTeX,
I derived a pipeline to export the reports to PDF, HTML, doc, text and wiki formats.
I also created some Jupyter Notebooks and some R Shiny websites for data visualization.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Genometra S.L.} % Job title
{Chief Data Scientist} % Organization
{Valencia - Spain} % Location
{2010 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
I co-founded the company.
I set it up as an spin-off company of the CIPF research center where I was working.
I carried out all the foundations administrative formalities and legal agreements.
}
\item {
I supervised a team of 3 technical staff (computer scientist, biologist and statistician)
and one commercial. 
I did train them at the beginning and keep them up to date with the latest technologies in Bioinformatics.
We also had several students and apprentices which I supervised.
}
\item {
At the beginning the company was marketing some of the software we had developed
in the research center for the preprocessing of raw genomic data. 
Later, we developed our own internal pipelines, software and methodologies
and we provided consulting services, training, and software and data base customization.
}
\item{
I developed several R packages, some of them contributed to public repositories as CRAN or Bioconductor.
I also developed several pipelines using Python and Linux shell script.
All this software was used to preprocess raw genomic data,
query databases or web services for extra biological information,
carrying out hypothesis testing or class predictions
and automatizing the creation of reports.
}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Principe Felipe Research Center (CIPF) - Computational Genomics Department} % Job title
{Head of the Biostatistics Unit} % Organization
{Valencia - Spain} % Location
{2005 - 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
I was head of the Biostatistics unit within the Bioinformatics department.
I supervised a team of other 3 statisticians.
}
\item {
In the Bioinformatics department we developed a suit of web tools for the analysis of genomic data.
Those tools have been now running form more than 15 years and can be found at www.babelomics.org.
Babelomics is the most used site in the world for functional genomics analysis.
I developed all the statistical back end of the application.
I did use R and Bioconductor libraries and also developed my own ones, now contributed to Bioconductor.
I did use Python, WEKA, AWK and many other open source code.
}
\item {
I developed or adapted several statistical methodologies to the analysis of gene expression data,
Sometimes for our tools or pipelines, sometimes for particular data analysis or collaborations:
linear and logistic regression, resampling and permutation methodologies, naive Bayes approaches,
multiple hypothesis testing, nested models, mixture models, sample size computation.
}
\item {
I wrote more than 50 scientific (pair reviewed) publications and a couple of book chapters.
I presented or organized more than 30 congresses and international workshops.
}
\item {
I have supervised several MSc students and one PhD.
}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{University of Valencia - Mathematics and Computer Science Departments} % Job title
{Par Time Lecturer} % Organization
{Valencia - Spain} % Location
{2009 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {Teaching Probability and Statistics to Undergraduate Mathematics students.}
\item {Teaching Statistics and Experimental Design to Biology and Economics students.}
\item {Teaching databases, R, Python, and Bash programming MSc students.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{University of Bristol - Social Medicine School} % Job title
{Epidemiologist} % Organization
{Bristol - U.K.} % Location
{2002 - 2004} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item {
Preprocessing and statistical analysis of large cohort studies.
I did use STATA, SAS and SPSS for all kind of descriptive statistics and plots,
survival analysis, regression analysis and hypothesis testing.}
\end{cvitems}        
}

%------------------------------------------------

\end{cventries}
