%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Selected Publications}

%% \end{cventries}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

\item
  \emph{Integrated gene set analysis for microRNA studies.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/27324197}{Bioinformatics
  (Oxford, England). 2016;}

\item
  \emph{Family-based genome-wide association study in Patagonia confirms
  the association of the DMD locus and cleft lip and palate.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/26331285}{European journal
  of oral sciences. 2015;}

\item
  \emph{Babelomics 5.0: functional interpretation for new generations of
  genomic data.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25897133}{Nucleic acids
  research. 2015; 43(W1):W117-21.}

\item
  \emph{Pathway network inference from gene expression data.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25032889}{BMC
  systems biology. 2014; 8 Suppl 2:S7.}

\item
  \emph{Four new loci associations discovered by pathway-based and
  network analyses of the genome-wide variability profile of
  Hirschsprung's disease.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/23270508}{Orphanet journal
  of rare diseases. 2012; 7:103.}

\item
  \emph{Large-scale transcriptional profiling and functional assays
  reveal important roles for Rho-GTPase signalling and SCL during
  haematopoietic differentiation of human embryonic stem cells.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/21937587}{Human molecular
  genetics. 2011; 20(24):4932-46.}

\item
  \emph{The MicroArray Quality Control (MAQC)-II study of common
  practices for the development and validation of microarray-based
  predictive models.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20676074}{Nature
  biotechnology. 2010; 28(8):827-38. NIHMSID: NIHMS235927}

\item
  \emph{Hypoxia promotes efficient differentiation of human embryonic
  stem cells to functional endothelium.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20049902}{Stem cells
  (Dayton, Ohio). 2010; 28(3):407-18.}

\item
  \emph{Initial genomics of the human nucleolus.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20361057}{PLoS genetics.
  2010; 6(3):e1000889.}

\item
  \emph{Multidimensional gene set analysis of genomic data.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20436964}{PloS one. 2010;
  5(4):e10348.}


\item
  \emph{Functional genomics of 5- to 8-cell stage human embryos by
  blastomere single-cell cDNA analysis.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/21049019}{PloS one. 2010;
  5(10):e13615.}

\item
  \emph{DNA methylation epigenotypes in breast cancer molecular
  subtypes.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20920229}{Breast cancer
  research : BCR. 2010; 12(5):R77.}

\item
  \emph{Gene set internal coherence in the context of functional
  profiling.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19397819}{BMC genomics.
  2009; 10:197.}

  \emph{SNOW, a web-based tool for the statistical analysis of
  protein-protein interaction networks.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19454602}{Nucleic acids
  research. 2009; 37(Web Server issue):W109-14.}

\item
  \emph{CLEAR-test: combining inference for differential expression and
  variability in microarray data analysis.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17597009}{Journal of
  biomedical informatics. 2008; 41(1):33-45.}

\item
  \emph{GEPAS, a web-based tool for microarray data analysis and
  interpretation.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/18508806}{Nucleic acids
  research. 2008; 36(Web Server issue):W308-14.}

\item
  \emph{Direct functional assessment of the composite phenotype through
  multivariate projection strategies.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/18652888}{Genomics. 2008;
  92(6):373-83.}

\item
  \emph{Functional profiling of microarray experiments using text-mining
  derived bioentities.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17855415}{Bioinformatics
  (Oxford, England). 2007; 23(22):3098-9.}

\item
  \emph{Prophet, a web-based tool for class prediction using microarray
  data.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17138587}{Bioinformatics
  (Oxford, England). 2007; 23(3):390-1.}

\item
  \emph{From genes to functional classes in the study of biological
  systems.} 
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17407596}{BMC
  bioinformatics. 2007; 8:114.}


\item
  \emph{The detection, treatment and control of high blood pressure in
  older British adults: cross-sectional findings from the British
  Women's Heart and Health Study and the British Regional Heart Study.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/16855626}{Journal of human
  hypertension. 2006; 20(10):733-41.}

\item
  \emph{Next station in microarray data analysis: GEPAS.}
  \href{http://www.ncbi.nlm.nih.gov//pubmed/16845056}{Nucleic acids
  research. 2006; 34(Web Server issue):W486-91.}

\item
  \emph{Clustering of risk factors and social class in childhood and
  adulthood in British women's heart and health study: cross sectional
  analysis.} Ebrahim S, \textbf{Montaner D}, Lawlor DA.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/15006898}{BMJ (Clinical
  research ed.). 2004; 328(7444):861.}

\end{enumerate}
