\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{Brief Report: Inhibition of miR-145 Enhances Reprogramming of
  Human Dermal Fibroblasts to Induced Pluripotent Stem Cells.} Barta T,
  Peskova L, Collin J, \textbf{Montaner D}, Neganova I, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/26418476}{Stem cells
  (Dayton, Ohio). 2016; 34(1):246-51.}
\item
  \emph{Family-based genome-wide association study in Patagonia confirms
  the association of the DMD locus and cleft lip and palate.} Fonseca
  RF, de Carvalho FM, Poletta FA, \textbf{Montaner D}, Dopazo J, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/26331285}{European journal
  of oral sciences. 2015;}
\item
  \emph{Babelomics 5.0: functional interpretation for new generations of
  genomic data.} Alonso R, Salavert F, Garcia-Garcia F,
  Carbonell-Caballero J, Bleda M, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25897133}{Nucleic acids
  research. 2015; 43(W1):W117-21.}
\item
  \emph{Therapeutic targets for olive pollen allergy defined by gene
  markers modulated by Ole e 1-derived peptides.} Calzada D, Aguerri M,
  Baos S, \textbf{Montaner D}, Mata M, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25553522}{Molecular
  immunology. 2015; 64(2):252-61.}
\item
  \emph{A new overgrowth syndrome is due to mutations in RNF125.}
  Tenorio J, Mansilla A, Valencia M, Martínez-Glez V, Romanelli V, et
  al. \href{http://www.ncbi.nlm.nih.gov//pubmed/25196541}{Human
  mutation. 2014; 35(12):1436-41.}
\item
  \emph{Understanding disease mechanisms with models of signaling
  pathway activities.} Sebastian-Leon P, Vidal E, Minguez P, Conesa A,
  Tarazona S, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25344409}{BMC systems
  biology. 2014; 8:121.}
\item
  \emph{A novel locus for a hereditary recurrent neuropathy on
  chromosome 21q21.} Calpena E, Martínez-Rubio D, Arpa J, García-Peñas
  JJ, \textbf{Montaner D}, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/24878226}{Neuromuscular
  disorders : NMD. 2014; 24(8):660-5.}
\item
  \emph{Quantitative modeling of clinical, cellular, and extracellular
  matrix variables suggest prognostic indicators in cancer: a model in
  neuroblastoma.} Tadeo I, Piqueras M, \textbf{Montaner D}, Villamón E,
  Berbegall AP, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/24216542}{Pediatric
  research. 2014; 75(2):302-14.}
\item
  \emph{Pathway network inference from gene expression data.} Ponzoni I,
  Nueda M, Tarazona S, Götz S, \textbf{Montaner D}, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/25032889}{BMC systems
  biology. 2014; 8 Suppl 2:S7.}
\item
  \emph{Differential gene-expression analysis defines a molecular
  pattern related to olive pollen allergy.} Aguerri M, Calzada D,
  \textbf{Montaner D}, Mata M, Florido F, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/23830385}{Journal of
  biological regulators and homeostatic agents. 2013; 27(2):337-50.}
\item
  \emph{Defining the genomic signature of totipotency and pluripotency
  during early human development.} Galan A, Diaz-Gimeno P, Poo ME,
  Valbuena D, Sanchez E, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/23614026}{PloS one. 2013;
  8(4):e62135.}
\item
  \emph{Four new loci associations discovered by pathway-based and
  network analyses of the genome-wide variability profile of
  Hirschsprung's disease.} Fernández RM, Bleda M, Núñez-Torres R, Medina
  I, Luzón-Toro B, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/23270508}{Orphanet journal
  of rare diseases. 2012; 7:103.}
\item
  \emph{The protease MT1-MMP drives a combinatorial proteolytic program
  in activated endothelial cells.} Koziol A, Gonzalo P, Mota A, Pollán
  Á, Lorenzo C, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/22859368}{FASEB journal :
  official publication of the Federation of American Societies for
  Experimental Biology. 2012; 26(11):4481-94.}
\item
  \emph{Extensive translatome remodeling during ER stress response in
  mammalian cells.} Ventoso I, Kochetov A, \textbf{Montaner D}, Dopazo
  J, Santoyo J. \href{http://www.ncbi.nlm.nih.gov//pubmed/22574127}{PloS
  one. 2012; 7(5):e35915.}
\item
  \emph{Large-scale transcriptional profiling and functional assays
  reveal important roles for Rho-GTPase signalling and SCL during
  haematopoietic differentiation of human embryonic stem cells.} Yung S,
  Ledran M, Moreno-Gimeno I, Conesa A, \textbf{Montaner D}, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/21937587}{Human molecular
  genetics. 2011; 20(24):4932-46.}
\item
  \emph{Differential lipid partitioning between adipocytes and tissue
  macrophages modulates macrophage lipotoxicity and M2/M1 polarization
  in obese mice.} Prieur X, Mok CY, Velagapudi VR, Núñez V, Fuentes L,
  et al. \href{http://www.ncbi.nlm.nih.gov//pubmed/21266330}{Diabetes.
  2011; 60(3):797-809.}
\item
  \emph{Functional genomics of 5- to 8-cell stage human embryos by
  blastomere single-cell cDNA analysis.} Galán A, \textbf{Montaner D},
  Póo ME, Valbuena D, Ruiz V, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/21049019}{PloS one. 2010;
  5(10):e13615.}
\item
  \emph{The MicroArray Quality Control (MAQC)-II study of common
  practices for the development and validation of microarray-based
  predictive models.} Shi L, Campbell G, Jones WD, Campagne F, Wen Z, et
  al. \href{http://www.ncbi.nlm.nih.gov//pubmed/20676074}{Nature
  biotechnology. 2010; 28(8):827-38. NIHMSID: NIHMS235927}
\item
  \emph{Babelomics: an integrative platform for the analysis of
  transcriptomics, proteomics and genomic data with advanced functional
  profiling.} Medina I, Carbonell J, Pulido L, Madeira SC, Goetz S, et
  al. \href{http://www.ncbi.nlm.nih.gov//pubmed/20478823}{Nucleic acids
  research. 2010; 38(Web Server issue):W210-3.}
\item
  \emph{Multidimensional gene set analysis of genomic data.}
  \textbf{Montaner D}, Dopazo J.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20436964}{PloS one. 2010;
  5(4):e10348.}
\item
  \emph{Hypoxia promotes efficient differentiation of human embryonic
  stem cells to functional endothelium.} Prado-Lopez S, Conesa A,
  Armiñán A, Martínez-Losa M, Escobedo-Lucea C, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20049902}{Stem cells
  (Dayton, Ohio). 2010; 28(3):407-18.}
\item
  \emph{Initial genomics of the human nucleolus.} Németh A, Conesa A,
  Santoyo-Lopez J, Medina I, \textbf{Montaner D}, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/20361057}{PLoS genetics.
  2010; 6(3):e1000889.}
\item
  \emph{FM19G11, a new hypoxia-inducible factor (HIF) modulator, affects
  stem cell differentiation status.} Moreno-Manzano V, Rodríguez-Jiménez
  FJ, Aceña-Bonilla JL, Fustero-Lardíes S, Erceg S, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19897487}{The Journal of
  biological chemistry. 2010; 285(2):1333-42.}
\item
  \emph{DNA methylation epigenotypes in breast cancer molecular
  subtypes.} Bediaga NG, Acha-Sagredo A, Guerra I, Viguri A, Albaina C,
  et al. \href{http://www.ncbi.nlm.nih.gov//pubmed/20920229}{Breast
  cancer research : BCR. 2010; 12(5):R77.}
\item
  \emph{Parallel changes in gene expression in peripheral blood
  mononuclear cells and the brain after maternal separation in the
  mouse.} van Heerden JH, Conesa A, Stein DJ, \textbf{Montaner D},
  Russell V, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19781058}{BMC research
  notes. 2009; 2:195.}
\item
  \emph{SNOW, a web-based tool for the statistical analysis of
  protein-protein interaction networks.} Minguez P, Götz S,
  \textbf{Montaner D}, Al-Shahrour F, Dopazo J.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19454602}{Nucleic acids
  research. 2009; 37(Web Server issue):W109-14.}
\item
  \emph{Gene set-based analysis of polymorphisms: finding pathways or
  biological processes associated to traits in genome-wide association
  studies.} Medina I, \textbf{Montaner D}, Bonifaci N, Pujana MA,
  Carbonell J, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19502494}{Nucleic acids
  research. 2009; 37(Web Server issue):W340-4.}
\item
  \emph{Gene set internal coherence in the context of functional
  profiling.} \textbf{Montaner D}, Minguez P, Al-Shahrour F, Dopazo J.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19397819}{BMC genomics.
  2009; 10:197.}
\item
  \emph{Cryptochrome-1 expression: a new prognostic marker in B-cell
  chronic lymphocytic leukemia.} Lewintre EJ, Martín CR, Ballesteros CG,
  \textbf{Montaner D}, Rivera RF, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19181792}{Haematologica.
  2009; 94(2):280-4.}
\item
  \emph{Analysis of chronic lymphotic leukemia transcriptomic profile:
  differences between molecular subgroups.} Jantus Lewintre E, Reinoso
  Martín C, \textbf{Montaner D}, Marín M, José Terol M, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/19127482}{Leukemia \&
  lymphoma. 2009; 50(1):68-79.}
\item
  \emph{Direct functional assessment of the composite phenotype through
  multivariate projection strategies.} Conesa A, Bro R, García-García F,
  Prats JM, Götz S, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/18652888}{Genomics. 2008;
  92(6):373-83.}
\item
  \emph{GEPAS, a web-based tool for microarray data analysis and
  interpretation.} Tárraga J, Medina I, Carbonell J, Huerta-Cepas J,
  Minguez P, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/18508806}{Nucleic acids
  research. 2008; 36(Web Server issue):W308-14.}
\item
  \emph{Babelomics: advanced functional profiling of transcriptomics,
  proteomics and genomics experiments.} Al-Shahrour F, Carbonell J,
  Minguez P, Goetz S, Conesa A, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/18515841}{Nucleic acids
  research. 2008; 36(Web Server issue):W341-6.}
\item
  \emph{Molecular profiling related to poor prognosis in thyroid
  carcinoma. Combining gene expression data and biological information.}
  Montero-Conde C, Martín-Campos JM, Lerma E, Gimenez G,
  Martínez-Guitarte JL, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17873908}{Oncogene. 2008;
  27(11):1554-61.}
\item
  \emph{CLEAR-test: combining inference for differential expression and
  variability in microarray data analysis.} Valls J, Grau M, Solé X,
  Hernández P, \textbf{Montaner D}, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17597009}{Journal of
  biomedical informatics. 2008; 41(1):33-45.}
\item
  \emph{Functional profiling of microarray experiments using text-mining
  derived bioentities.} Minguez P, Al-Shahrour F, \textbf{Montaner D},
  Dopazo J.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17855415}{Bioinformatics
  (Oxford, England). 2007; 23(22):3098-9.}
\item
  \emph{ISACGH: a web-based environment for the analysis of Array CGH
  and gene expression which includes functional profiling.} Conde L,
  \textbf{Montaner D}, Burguet-Castell J, Tárraga J, Medina I, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17468499}{Nucleic acids
  research. 2007; 35(Web Server issue):W81-5.}
\item
  \emph{FatiGO +: a functional profiling tool for genomic data.
  Integration of functional annotation, regulatory motifs and
  interaction data with microarray experiments.} Al-Shahrour F, Minguez
  P, Tárraga J, Medina I, Alloza E, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17478504}{Nucleic acids
  research. 2007; 35(Web Server issue):W91-6.}
\item
  \emph{Evidence for systems-level molecular mechanisms of
  tumorigenesis.} Hernández P, Huerta-Cepas J, \textbf{Montaner D},
  Al-Shahrour F, Valls J, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17584915}{BMC genomics.
  2007; 8:185.}
\item
  \emph{Functional profiling and gene expression analysis of chromosomal
  copy number alterations.} Conde L, \textbf{Montaner D},
  Burguet-Castell J, Tárraga J, Al-Shahrour F, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17597935}{Bioinformation.
  2007; 1(10):432-5.}
\item
  \emph{From genes to functional classes in the study of biological
  systems.} Al-Shahrour F, Arbiza L, Dopazo H, Huerta-Cepas J, Mínguez
  P, et al. \href{http://www.ncbi.nlm.nih.gov//pubmed/17407596}{BMC
  bioinformatics. 2007; 8:114.}
\item
  \emph{Prophet, a web-based tool for class prediction using microarray
  data.} Medina I, \textbf{Montaner D}, Tárraga J, Dopazo J.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/17138587}{Bioinformatics
  (Oxford, England). 2007; 23(3):390-1.}
\item
  \emph{The detection, treatment and control of high blood pressure in
  older British adults: cross-sectional findings from the British
  Women's Heart and Health Study and the British Regional Heart Study.}
  Patel R, Lawlor DA, Whincup P, \textbf{Montaner D}, Papacosta O, et
  al. \href{http://www.ncbi.nlm.nih.gov//pubmed/16855626}{Journal of
  human hypertension. 2006; 20(10):733-41.}
\item
  \emph{BABELOMICS: a systems biology perspective in the functional
  annotation of genome-scale experiments.} Al-Shahrour F, Minguez P,
  Tárraga J, \textbf{Montaner D}, Alloza E, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/16845052}{Nucleic acids
  research. 2006; 34(Web Server issue):W472-6.}
\item
  \emph{Next station in microarray data analysis: GEPAS.}
  \textbf{Montaner D}, Tárraga J, Huerta-Cepas J, Burguet J, Vaquerizas
  JM, et al. \href{http://www.ncbi.nlm.nih.gov//pubmed/16845056}{Nucleic
  acids research. 2006; 34(Web Server issue):W486-91.}
\item
  \emph{Self-reported smoking cessation interventions were not
  associated with quitting in older women.} Schroeder K, Lawlor DA,
  \textbf{Montaner D}, Ebrahim S.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/16713525}{Journal of
  clinical epidemiology. 2006; 59(6):622-8.}
\item
  \emph{Selective pressures at a codon-level predict deleterious
  mutations in human disease genes.} Arbiza L, Duchi S, \textbf{Montaner
  D}, Burguet J, Pantoja-Uceda D, et al.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/16584746}{Journal of
  molecular biology. 2006; 358(5):1390-404.}
\item
  \emph{How acceptable are innovative health-care technologies? A survey
  of public beliefs and attitudes in England and Wales.} Calnan M,
  \textbf{Montaner D}, Horne R.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/15743645}{Social science \&
  medicine (1982). 2005; 60(9):1937-48.}
\item
  \emph{Coronary heart disease prevention in clinical practice: are
  patients with diabetes special? Evidence from two studies of older men
  and women.} Emberson JR, Whincup PH, Lawlor DA, \textbf{Montaner D},
  Ebrahim S. \href{http://www.ncbi.nlm.nih.gov//pubmed/15772196}{Heart
  (British Cardiac Society). 2005; 91(4):451-5.}
\item
  \emph{Clustering of risk factors and social class in childhood and
  adulthood in British women's heart and health study: cross sectional
  analysis.} Ebrahim S, \textbf{Montaner D}, Lawlor DA.
  \href{http://www.ncbi.nlm.nih.gov//pubmed/15006898}{BMJ (Clinical
  research ed.). 2004; 328(7444):861.}
\end{enumerate}
